Machine learning algorithm to predict activity quality
========================

### Data loading

```{r}
ds <- read.csv("pml-training.csv")
```

### Deleting columns where amount of NAs more than 60%

```{r}

NAvaluesAllowed <- length(rownames(ds)) * 0.6
cols <- apply(ds, 2, function(x) 
    length(which(!is.na(x))) > NAvaluesAllowed)
    
ds <- ds[,cols]    
```

### Getting rid of variables with near zero variation

```{r echo = FALSE}
library(caret)
nzv <- nearZeroVar(ds)
```

### Remove timestamp, user, num_window column

```{r}
ds <- ds[, -nzv]
ds <- ds[,-grep("timestamp",colnames(ds))]
ds <- ds[,-1] #remove X column
ds <- ds[,-1] #remove user_name column
ds <- ds[,-1] # remove num_window column
```

### Dividing given dataset on train and test portions

```{r}

inTrain = createDataPartition(ds$classe, p = 0.6)[[1]]
training = ds[ inTrain,]
testing = ds[-inTrain,]
```

### Building prediction model using random forest method

```{r}

library(randomForest)

model1 <- randomForest(classe ~ ., data = training, importance=TRUE)
```    

### Reading test data and predicting using our model

```{r}
tds <- read.csv("pml-testing.csv")

colnames <- colnames(training)
tdsa <- tds[,colnames[-53]]
    
ptds <- predict(model1, tdsa)


```
